Turbulence in compact to giant HII regions

### 2022-05-16 strucfunc_paper.tex
Write something on large scale inhomogeneity

>>>>

At scales larger than \(L/2\),
we see a variety of different shapes for the structure functions
of our sample regions. 
In some cases,
such as Carina and Hubble~X,
\(B(r)\) remains flat at a value of \(\approx 2\sigma^2\),
which is consistent with uncorrelated homogeneous fluctuations
at the largest scales.
For other regions,
such as the Orion Nebula (both inner and outer) and 30~Doradus,
there is a clear downturn in \(B(r)\) at the largest separations.
As discussed above in section~\ref{sec:limit-model-struct},
this is what would be expected if the velocity fluctuations
were inhomogeneous, with a larger amplitude in the center of the map
and a smaller amplitude in the outskirts.
A similar behavior, although not so marked, is shown by
Hubble~V and NGC~595.
The Orion Nebula is a particularly interesting case
since the \(\sigma^2\) derived from the high-resolution dataset of the inner nebula on scales \(\approx \SI{0.1}{pc}\)
is roughly twice as large as that derived from the lower resolution
dataset of the Extended Orion Nebula on scales \(\approx \SI{1}{pc}\)
(compare panels a and b of Figure~\ref{fig:strucfunc-fit-Galactic}).
